Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
update compilation section 7

The first idea is to tag every protocol message with a BGP community value that encodes the state of each automaton when advertising a route to a neighbor. Routers can then allow route advertisements that correspond to an edge in the Product Graph and block those that don't.
%This ensures that any path computed by BGP will be a valid path in the Product Graph, and thus is allowed by the policy.
For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router $S1$ will allow a route advertisement from its neighbor $P1$ and also from neighbor $P2$. If it uses the path provided by neighbor $P1$, then it will add the tag $(1,0)$ before informing its neighbors about this route. On the other hand, if it uses neighbor $P2$, then it will add the tag $(0,1)$ instead.

\para{Preference Search}
The second idea is to have each router totally order advertisements from neighbors. For example, to satisfy the policy that leaving through $\sf{P1}$ is preferred to leaving through $\sf{P2}$, router $S1$ should prefer a message it hears from $P1$ over one from $P2$. Similarly, router $A1$ should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
%In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use. Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
Propane introduced a conservative, yet effective algorithm for determining route preferences based on the following observation about the structure of the Product Graph:

\begin{defn}
Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$. Intuitively $m \geq_{rank} n$ means that paths ending at PGIR node $m$ are no better than paths ending at $n$.
%
\end{defn}
\noindent
%

@@

If each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ if $m' \leq m$.
%
For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received in state $(0,1)$.

Notice also that in the abstract product graph the inequality $(S,0,1) \leq (S,1,0)$ holds. This leads us the the following observation:

\begin{lem}
\label{lem:preference}
$m \leq m'$ in the concrete product graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract product graph under the lifted graph homomorphism $f_{pg}$.
\end{lem}

Lemma~\ref{lem:preference} gives us reason to believe that we can perform compilation over the abstract product graph and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.

@@

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies.
%
For prefix $0.0.0.0/[0..32]$, the spine routers will match advertisements from peer $P1$ and $P2$. The match for $P1$ is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from $P1$ is available the spine uses this and attaches the community tag $(1,0)$ and advertises the route to all its peers. If only an advertisement from the backup $P2$ is available, then it attaches the tag $(0,1)$ and advertises this to all peers instead.
%
There is also additional policy for the Product Graphs from constraints for the local and global prefixes. In the template configuration, it matches any global prefix from any internal peer and re-advertise the route to all of its peers. For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers (thus implementing the Local constraint). The concrete configurations have a similar configuration for each local and global prefix.

>>>>

The first idea is to tag every protocol message with a BGP community that encodes the state of each DFA when advertising a route to a neighbor. Routers then allow route advertisements that correspond to an edge in the Product Graph and block those that do not.
For example, in the concrete Product Graph in figure~\ref{fig:example-compilation}, router S1 will allow an advertisement from its neighbors N1 and N2. If it uses the path advertised by neighbor N1, then it will add the tag $(1,0)$ before sending this to its neighbors. If it uses neighbor N2, then it will add the tag $(0,1)$ instead.

\para{Preference Search}
The second idea is to have each router totally order advertisements from neighbors. For example, to satisfy the policy that leaving through N1 is preferred to leaving through N2, router S1 should prefer a message it hears from N1 over N2. Similarly, router A1 should prefer routes tagged with $(1,0)$ over those tagged with $(0,1)$.
%In general, because BGP is distributed, each router does not have a full view of the entire network when choosing which path to use. Because finding a collection of preferences to ensure correct end-to-end behavior for all failures is a hard problem,
Propane introduced a conservative search strategy for determining route preferences. To make this work for abstract topologies, we modify the search based on the following observation about the structure of the Product Graph:

\begin{defn}
Let $m \geq_{rank} n$ be a relation over Product Graph vertices that holds iff $P(n) = \emptyset$ or $\min P(m) \geq \min P(n)$. Intuitively $m \geq_{rank} n$ means that paths ending at Product Graph node $m$ are no better in terms of preference than paths ending at $n$.
%
\end{defn}
\noindent
%

@@

If we determine that each router has a total order with respect to the simulation relation ($\leq$) for its corresponding Product Graph nodes, then we can simply sort the nodes and prefer advertisements from peers of node $m$ over those of node $m'$ whenever $m' \leq m$. This condition ensures that BGP devices will converge to the most preferred paths in the network even when failures occur.
%
For example, in the concrete product graph the inequality $(S1,0,1) \leq (S1,1,0)$ holds since nodes on the left side of the product graph can always match transitions made on the right hand side with respect to the $\geq_{rank}$ relation. This relation does not hold the other way around since $(S1,0,1) \ngeq_{rank} (S1,1,0)$. Therefore, advertisements received at $S1$ in state $(1,0)$ must be preferred to those received at $S1$ in state $(0,1)$.
%
Notice that in the abstract product graph $(S,0,1) \leq (S,1,0)$ also holds. This leads us the the following observation:

\begin{lem}
\label{lem:preference}
$m \leq m'$ in the concrete Product Graph iff $f_{pg}(m) \leq f_{pg}(m')$ in the abstract Product Graph.
\end{lem}

This gives us reason to believe that we can perform compilation over the abstract product graph directly and ensure that the inferred device-level preferences will be correct when instantiating the template with a concrete network.

@@

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers. If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertise the route to all of its peers ($*$). For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.
